---
title: "NHL Shot Data Blank Canvas"
output: html_notebook
---

Ok, here's the bare minimum you need to adjust or make the model into pretty pictures. Have fun! 


Packages for your graphing pleasure: 

```{r}
#Necessary packages installed, so uncomment this code as needed for your package availability
#install.packages("tidyverse")
#install.packages("RCurl")
#install.packages('fastDummies')
library(tidyverse)
library(RCurl)
library(grid)
library(tidyverse)
library(mosaic)
```

Here's the dataset you'll need (downloaded from the Drive)


```{r}
FinalCleanData <- readRDS("FinalWorkingShotData.rds")
FinalCleanData
```

It already has the xSave values fitted to it, but in case you want to modify or edit or are curious, here's what I used to make them (feel free to change):

```{r}
xSave2 <-glm (save_dummy ~ DistanceToNet + DumpInDummy + BehindNetDummy +  ScoreStateForGoalieAtShot + GameShotNumber + SecondsSinceLastShot + Rebound + DaysSinceLastGame + factor(period) + factor(shotType) + factor(goalie_team_name) + factor(shooter_team_name), data = FinalCleanData, family = "binomial")
summary(xSave2)
```


And fitting them to the data:

```{r}
FinalCleanData$xSave <- fitted(xSave2)
```


Alright, from here you can go nuts! Adjust the model, make pretty pictures, whatever you are tasked to do/want to do. Have fun, and if you wanna see the ugly code for this, ask away! 
